---
title: "Project 1"
author: "Ha Bui"
date: "Exploratory Data Analysis - Project 1"
header-includes:
   - \usepackage{bbm}
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dslabs)
library(tidyverse)
library(dplyr)
```

# Data Appendix:
## Dataset: 
Electric power consumption


## Description: 
Measurements of electric power consumption in one household with a one-minute sampling rate over a period of almost 4 years. Different electrical quantities and some sub-metering values are available.

## Variables
The following descriptions of the 9 variables in the dataset are taken from the UCI web site:

* Date: Date in format dd/mm/yyyy

* Time: time in format hh:mm:ss

* Global_active_power: household global minute-averaged active power (in kilowatt)

* Global_reactive_power: household global minute-averaged reactive power (in kilowatt)

* Voltage: minute-averaged voltage (in volt)

* Global_intensity: household global minute-averaged current intensity (in ampere)

* Sub_metering_1: energy sub-metering No. 1 (in watt-hour of active energy). It corresponds to the kitchen, containing mainly a dishwasher, an oven and a microwave (hot plates are not electric but gas powered).

* Sub_metering_2: energy sub-metering No. 2 (in watt-hour of active energy). It corresponds to the laundry room, containing a washing-machine, a tumble-drier, a refrigerator and a light.

* Sub_metering_3: energy sub-metering No. 3 (in watt-hour of active energy). It corresponds to an electric water-heater and an air-conditioner.


# Load and Clean data
```{r}
file1 = "C:/Users/ha/OneDrive - Vassar College/classes/Coursera/Data Analysis/Exploratory Data with R/household_power_consumption.txt"
data <- read.csv2(file1, header = TRUE, na.strings = "?")
df <- subset(data, Date%in%c("1/2/2007", "2/2/2007"))
df <- mutate(df, DateTime=as.POSIXct(paste(as.Date(df$Date, format="%d/%m/%Y"),
         df$Time, sep=" ")))
```

# Creating plots

```{r}
plot1 <-hist(as.numeric(df$Global_active_power), col="red",
             xlab="Global Active Power (kilowatts)", ylab="Frequency", 
             main="Global Active Power")
dev.copy(png, file = "plot1.png", height=480, width=480)
dev.off()
```
```{r}
plot2 <- plot(df$Global_active_power~df$DateTime, type="l", ylab="Global Active Power (kilowatts)", xlab="")
dev.copy(png, file = "plot2.png", height=480, width=480)
dev.off()
```


```{r}
plot3 <- with(df, {
  plot(Sub_metering_1~DateTime, type="l", ylab="Global Active Power (kilowatts)", col="black", xlab="")
  lines(Sub_metering_2~DateTime, col="red")
  lines(Sub_metering_3~DateTime, col="blue")
  legend("topright"
       , col=c("black","red","blue")
       , c("Sub_metering_1  ","Sub_metering_2  ", "Sub_metering_3  ")
       ,lty=c(1,1), lwd=c(1,1))
  })
dev.copy(png, file = "plot3.png", height=480, width=480)
dev.off()

```

```{r}
par(mfcol=c(2, 2), mar=c(4, 4, 2, 1), oma=c(0, 2, 0, 0))
plot4 <- with(df, {
  plot(Global_active_power~DateTime, type="l", ylab="Global Active Power (kilowatts)", xlab="")
  plot(Sub_metering_1~DateTime, type="l", ylab="Global Active Power (kilowatts)", col="black", xlab="")
  lines(Sub_metering_2~DateTime, col="red")
  lines(Sub_metering_3~DateTime, col="blue")
  legend("topright"
       , col=c("black","red","blue")
       , c("Sub_metering_1  ","Sub_metering_2  ", "Sub_metering_3  ")
       ,lty=c(1,1), cex=0.5)
  plot(Voltage~DateTime, type="l", ylab="Voltage (volt)", xlab="")
  plot(Global_reactive_power~DateTime, type="l", ylab="Global Reactive Power (kilowatts)", xlab="")
})
dev.copy(png, file = "plot4.png", height=480, width=480)
dev.off()

```